---
title: "Cleaning "
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
require(dplyr)
require(ggplot2)
```

This document is a brief summary of the surface cleaning experiment performed by Beth in the public health labs at the University of Leeds.

# Experimental set up


5 coupons of PVC (3 x 3cm)  were inoculated with with 1ml of *S. aureus* solution at $1 \times 10^9$ cfu/ml and allowed to dry for 60 min in a stable condition (inside a fume cupboard - would need to measure typical humidity or look to see if those data exist).

The coupons were then cleaned with one of the following:

- Disinfectant wipe (Tuffie - 70% solution of Isopropyl Alcohol BP), 
- detergent wipe (Tuffie - Contains amongst other ingredients less than 5% cationic surfactants, amphoteric surfactants and EDTA (Vernacare, 2018). They contain a mixture of non-ionic constituents at neutral pH), 
- distilled water wipe (Tuffie - alcohol wipes, after being dried, washed and re-soaked in distilled water.)
- no cleaning - control

The surfaces were then sampled using a cotton swab at the following time-points: $\{0, 1, 2, 4, 7, 24\}$.

**NB** The control samples were diluted by $10^$3 before plating out due to high concentrations anticipated.


```{r}
# Read in cleaningExptBeth.csv from LabData

df<-read.csv("../LabData/cleaningExptBeth.csv")

#Plot the data with ggplot2


df$TimeAfterCleaning <- as.numeric(df$TimeAfterCleaning)

df%>%
    filter(Count > 0) %>%
    ggplot(aes(x=TimeAfterCleaning,y=Count,color=CleaningType))+
    #geom_point(alpha=0.3)+
    #Add errorbars to the points using stat_summary
    stat_summary(fun.y = mean, geom = "point") + 
    stat_summary(fun.data = mean_se, geom = "errorbar")+
    scale_color_brewer(palette="Set1")+
    scale_y_continuous(trans="log10")+
    facet_grid(CleaningType~.,scales="free")+
    hrbrthemes::theme_ipsum()+
    labs(x="Time after cleaning (hours)",y="CFU",title="Cleaning Experiment")+
    theme(legend.position="",legend.title=element_text(face="bold"))
```

---

## Governing equations

We consider a number of models which potentially represent the phyisical action of cleaning method on hands. Below we propose three such models, with increasing complexity

- Option 1. Re-growth on hands but no recontamination from contacts 

$$\dfrac{dy}{dt}=ry-d \exp(-gt)$$
where $r$ is the regrowth rate per unit time $t$, $d$ is the maximum efficacy of cleaning method and $g$ is the decay rate induced by the cleaning method with units $^{-t}$.

- Option 2. Re-growth on hands and recontamination from surface contacts over time

$$\dfrac{dy}{dt}=l + ry-d \exp(-gt)$$

